Capabilities, MMIO and Robust Safety

### 2020-03-24 capability-meetings-notes/10-03/main.tex
MMIO meeting notes: tweak

Note that to link scenario 2 to scenario 1, we need a slightly adapted version
of the robust safety theorem stated above where the initial trace is allowed to
not be empty, but rather just satisfy $P(t)$, but that should not cause any
problems.

Note as well that here, if the boot-code performs I/O, it is required to satisfy
the invariant $P$ on the trace. If needed, one could come up with a more general
theorem statement, where the boot code is allowed to perform arbitrary I/O, and
where $P$ is thus only enforced on the suffix of the trace \emph{after} the boot
code has run...

>>>>

Note that to link scenario 2 to scenario 1, we need a slightly adapted version
of the robust safety theorem stated previously, where the initial trace is
allowed to not be empty, but rather just satisfy $P(t)$, but that should not
cause any problems.

Note as well that if the boot-code performs I/O, then it is required to preserve
the invariant $P$ on the trace. If needed, one could come up with a more general
theorem statement, where the boot code is allowed to perform arbitrary I/O, and
where $P$ is thus only true of the suffix of the trace for events that occur
\emph{after} the boot code has run...
